The following are the packaging requirements that specify how the delivered product will be packaged for delivery to the end-user.

\subsection{Requirement Name}
\subsubsection{Description}
\begin{enumerate}
  \item	The structure of the system: The raspberry pi and associated circuitry will be in a protected enclosure with a tripod stand to keep it above ground level.
  \item Components of the system: The delivered product will be in form of a ground based sensor device and a web application. The ground based sensor device shall capture the acoustic signals and provide it to the system and the web based application would show the results of the inputs
  \item Weight of the system: The ground based drone detection sensor system shall weigh less than 50 lbs. The only hardware system that is presented to the customer is the ground based sensor system hence there is a weight limit associated to it.
  \item User manual:The user manual shall be provided to the customer which would have a step by step set up guideline to start the system.
 \item Scope of source code: Source code shall not be given to customers	and shall be disputed upon and owned by any number of us, but it won't be something customers can own immediately. They have to pay



\end{enumerate}
\subsubsection{Source}
\begin{enumerate}
  \item James: The structure of the system
  \item Sanyogita: Components of the system
  \item Sanyogita: Weight of the system
  \item Sanyogita: Presence of user manual.
  \item Augustine: Scope of source code.
\end{enumerate}
\subsubsection{Constraints}
Detailed description of applicable constraints...
\subsubsection{Standards}
\begin{itemize}
    \item  2. Components of the system: In order to run the web application, the user should have access to internet.
   \item 5. Scope of source code: Copyright laws
\end{itemize}
 
\subsubsection{Priority}
\begin{enumerate}
  \item The structure of the system: Medium
  \item Components of the system: Critical
  \item Weight of the system: High
  \item Presence of user manual: High
  \item Scope of source code:High
\end{enumerate}
